\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-09 ccs/ex.tex
nit

\subsection{Comparison with garbled circuits}
\label{sec:oblivm}
We show that it is critical to use a mix of arithmetic and boolean circuits  for performance.
 Previous work has observed that Yao's garbled circuits do not scale to machine learning examples that require a large number of multiplications~\cite{aby,tasty,autoS,secureml,minionn,chameleon}.
Indeed, this is one of the main drivers behind the development of various specialized \mpc protocols in previous works~\cite{secureml,minionn,shafindss} (we compare against them in~\sectionref{eval}) .
Here, we empirically demonstrate the performance benefits of mixed computations over boolean-only compute by comparing with state of the art Yao-based compilers CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm}.

@@

\section{Cryptographic cost-awareness}
 \label{sec:ccc}
In this section, we explain various heuristics that \tool uses to split
the computation in a program into arithmetic and
boolean parts. While finding an optimum split  is an NP-hard problem (the predicates in {\tt if} statements can have arbitrary non-linear arithmetic),
\tool uses heuristics based
on empirical micro-benchmarking that  perform well in practice (Section~\ref{sec:eval}).

>>>>

\subsection{Comparison with garbled circuits}
\label{sec:oblivm}
We show that it is critical to use a mix of arithmetic and boolean circuits  for performance.
 Previous works have observed that Yao's garbled circuits do not scale to machine learning examples that require a large number of multiplications~\cite{aby,tasty,autoS,secureml,minionn,chameleon}.
Indeed, this is one of the main drivers behind the development of various specialized \mpc protocols in previous works~\cite{secureml,minionn,shafindss} (we compare against them in~\sectionref{eval}) .
Here, we empirically demonstrate the performance benefits of mixed computations over boolean-only compute by comparing with state of the art Yao-based compilers CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm}.

@@

\section{Cryptographic cost-awareness}
 \label{sec:ccc}
In this section, we explain various heuristics that \tool uses to split
the computation in a program into arithmetic and
boolean parts. Since finding an optimum split  is an NP-hard problem (the predicates in {\tt if} statements can have arbitrary non-linear arithmetic),
\tool uses heuristics  that  perform well in practice (Section~\ref{sec:eval}).
